Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-03-20 ms.tex
I made a crude initial time series for the 2016-06-12 data using python's photutils.

>>>>

\section{Time Series}

As an initial start, I created a time series for the night of UT 2016-06-12.
I used aperture photometry with a source radius of 4 pixels, an inner aperture annulus of 5 pixels and an outer aperture radius of 8 pixels for the background.
I choose 6 reference stars of similar brightness and which were nearby the source on the CCD.
I use the \texttt{photutils} python package for the aperture photometry.
The resulting raw time series can be seen in \ref{fig:initTseries}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{initial_t_series.pdf}
\caption{Quick raw time series for UT 2016-06-12. No aperture centering was done (there were fixed apertures with time).
No bias or flat field corrections were applied.}\label{fig:initTseries}
\end{centering}
\end{figure}
